### 2021-05-27 README.Rmd
encapsulated the main MSE within do_MSE, No EWN

* 2021-05-07 0.0.0.2500 Some relatively large changes this time. I have pulled most of the code used to run the MSE into a separate source file 'MSE_source.R'. You can find all required files in  \Dropbox\National abalone MSE\aMSE_files\scenarios. I have moved TasmanianHS.R into tasdata as it is currently common to different uses. I will endeavour to generalize the contents of MSE_source.R to turn it into a function that can be included in the package. Then any changes made there will flow naturally to other instances of each scenario file. Also, now there is a minimu requirement of 2 SAU but each SAU can have a minimum of 1 population.

* 2021-04-20 0.0.0.2900 Continuing process of modifying the core functions to allow for the numbers-at-size prior to fishing and the midyear-exploitB (midyexpB) to be included in teh zoneD object. doprojection still requires fursther modification to account for applying to chosen HCR and HS to the completed conditioned zoneDD to provide the first year of expected catches in the projections (which are to be defined by teh conditoned data prior to projections beginning).

@@

This is an example which illustrates the generation of an initial equilibrium, which then goes on to apply an early version of the Tasmania MCDA using only 100 replicates (that bit takes about 15 seconds on my computer, hence 2.5 minutes for 1000). It uses built in data-sets but usually you would read in a control file, which would contain the name of the biological datafile describing each population.

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario ----------------------------------------------------
source(paste0(ddir,"aMSEUse/scenarios/MSE_Source.R"))

# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "aMSE"
# )

@@

```{r }
str(zoneDP,max.level=1)

>>>>

* 2021-05-27 aMSE 0.0.0.2400 Have encapsulated the bulk of running the MSE for a particular scenario into the function 'do_MSE'. Check out its help page but also see it in action in the example within this readme file or in the new version of first_use_saudata.R in ~Dropbox\National abalone MSE\aMSE_files\scenarios\HS652510. I have also updated the aMSE_0.0.0.2400.tar.gz file. Any issues get in touch.

@@

This is an example which illustrates the generation of an initial equilibrium, which then goes on to apply an early version of the Tasmania MCDA using only 50 replicates (that bit takes about 15 seconds on my computer, hence 2.5 minutes for 1000). It uses built in data-sets but usually you would read in a control file, which would contain the name of the biological datafile describing each population.

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario ----------------------------------------------------
#source(paste0(ddir,"aMSEUse/scenarios/MSE_Source.R"))
out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,
              hcrfun=mcdahcr,sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
              getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=32,
              cleanslate=TRUE,verbose=TRUE,doproject=TRUE,ndiagprojs=3)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(out$starttime),
                endtime=as.character(out$projtime))
glb <- out$glb
runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
                   "  replicates = ",glb$reps,",   years projected = ",glb$pyrs,
                   "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
                   "  Randomseed for conditioning = ",out$ctrl$randseed)

# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "hs652510"
# )

@@

```{r }
str(out$zoneDP,max.level=1)
